\textbf{Masterclass Assignment Documentation}

### 2018-01-11 docs/Joe_Withers_Masterclass_Docs.tex
updated documentation

>>>>

The source material\cite{crassin_neyret_sainz_green_eisemann_2011} also describes a method for anisotropic mip-mapping of the 3D texture, storing a version of the texture for each directional axis, which improves visual accuracy when cone tracing. Whilst I could have implemented this with the dense 3D textures I was using, I opted to use OpenGL's built in mip-mapping to save time.
